---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```


# jfbpack
[Check out the website](https://jfberner.github.io/jfbpack) 
<!-- badges: start -->
[![R-CMD-check](https://github.com/jfberner/jfbpack/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/jfberner/jfbpack/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->


The goal of jfbpack is to experiment and learn how to create an R package, hopefully the first of many the author publishes. It contains a single function that gives one of three diversity indices of a given vector.

## Installation

You can install the development version of jfbpack like so:


``` r
remotes::install_github('jfberner/jfbpack)
```

## Example

This is a basic example which shows you how to use the my_diversity function:

```{r example}
library(jfbpack)
com <- c(1,2,3,50,16)

my_diversity(com, 'shannon')
```
